Overview and Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-02-26 WSSSPE1_report/WSSSPE1_summary_report.tex
reformulate sentence
extend sentence a bit

Is there a role for the growing science of the team science field in this? There
is overlap between the communities, with support for virtual organizations,
tool development, etc. How can we make time in an already crowded schedule to
introduce these topics to students? Should they be introduced through lab
classes as in ``real sciences''?

@@

There was debate that while some of the basics of computing may be fairly
similar, that the tools commonly used for computing have changed quite
significantly. Reference was made to Perl, which was commonly used, giving way
to whole new languages, such as Python, for gluing things together and how this
induces many students into entirely rewriting the scaffolding, leaving the old
to rot and the experiments to become non-reproducible as the tools change.
Jason Riedy stated that he had been guilty of this in the past. There was
discussion of this tendency along with the enormous differences in the speed and
ease of sharing---having to ship tapes around (GCC, Emacs, etc) as opposed to
the immediate sharing of the latest development in CVS, Subversion, Git,
Mercurial, Bazaar, etc.

>>>>

What is the role for the growing field of team science? There
is overlap between the communities, with support for virtual organizations,
tool development, etc. How can we make time in an already crowded schedule to
introduce these topics to students? Should they be introduced through lab
classes as in ``real sciences''?

@@

There was debate that while some of the basics of computing may be fairly
similar tools commonly used for computing have changed quite
significantly. Reference was made to Perl, which was commonly used, giving way
to whole new languages, such as Python, for gluing things together and how this
induces many students into entirely rewriting the scaffolding, leaving the old
to rot and the experiments to become non-reproducible as the tools change.
Jason Riedy stated that he had been guilty of this in the past. There was
discussion of this tendency along with the enormous differences in the speed and
ease of sharing---having to ship tapes around (GCC, Emacs, etc) as opposed to
the immediate sharing of the latest development online, using revision control
systems like CVS, Subversion, Git, Mercurial, Bazaar, etc.
